DDSAnalytics  - Employee Trends

### 2018-04-16 msds6371-group-project-kaggle.Rmd
Commit changes

### Parameters
* Estimates - refer to model #2 above for the parameter estimates
* Interpretation
* Confidence Intervals - refer to Image 007 for 95% confidence interval for the individual parameters.

>>>>

### Parameters
* Estimates - refer to model #2 above for the parameter estimates
* Interpretation
    * Reference category: BrkSide+Edwards
        * beta0 - The median SalePrice of houses that are located either in the Neighborhoods of BrkSide or Edwards,and has the GrLivArea of 1
        * beta1 - Doubling the GrLivArea is associated with 1.796 increase of the median SalePrice, roughly a 79.6% increase in median price.
    * Category: NAmes
        * beta2 - The difference between the median price of a house in NAmes and BrkSide+Edwards neighborhoods, that has a GrLivArea of 1
        * beta4 - The difference in slope of the regression line of LogGrLivArea when Neighborhood is NAmes and the slope when the Neighborhood is equal to BrkSide+Edwards.
    * Category: Others
        * beta3 - The difference between the median price of a house in Others and BrkSide+Edwards neighborhoods, that has a GrLivArea of 1
        * beta5 - The difference in slope of the regression line of LogGrLivArea when Neighborhood is Others and the slope when the Neighborhood is equal to BrkSide+Edwards.
* Confidence Intervals - refer to Image 007 for 95% confidence interval for the individual parameters.
